%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
\newcommand\research{TP1 Group}
\newcommand\country{Siegen, Germany }
\newcommand\uni{Universit\"{a}t Siegen }

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Matthew}{Black}
%\position{Software Architect{\enskip\cdotp\enskip}Security Expert}
\address{Easter Banknock, Denny, FK6 5NA, United Kingdom}

\mobile{(+44) 7446 949025}
\github{mbr-phys}
%\email{matthewkblack@protonmail.com}
\email{Matthew.Black@uni-siegen.de}
%\homepage{www.posquit0.com}
%\linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {\research}
  {\uni \\ \country}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application for Wissenschaftliche/r Mitarbeiter/in - Theoretische Teilchenphysik (2506)}
% How the letter is opened
\letteropening{To whom it may concern,}
% How the letter is closed
\letterclosing{Thank you for your time and consideration, I look forward to hearing from you. \\ Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae, Academic Transcript, Masters Thesis}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Matthew Black~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\vspace{-20pt}
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I began my doctoral project at Siegen in March 2021.
Previously, I finished my undergraduate degree August 2020 studying Theoretical Physics (MPhys) at the Durham University in the UK where I achieved a Class I (Honours), which is the highest degree rank possible. 
Durham University is one of the oldest universities in the UK, and consistently ranks within the top 10 UK universities both overall and specifically for its Physics department.
I have spent the previous years focusing on particle physics, through studying several courses on the subjects of quantum mechanics and particle physics.
These courses relate closely to the fundamental physics research undertaken at the famous CERN and its Large Hadron Collider, and they have prepared me for theoretical physics studies of the predictions for many of the processes that are observed and measured at the LHC. 
During my Masters thesis, I worked on a research project within this area and since the completion of my thesis, I continued to work on this project with others to develop a research paper performing statistical analysis of the 2HDM using the program package flavio.
%During my third year, I looked into the difficulties of understanding and predicting the behaviours of QCD in a project to model the inter-quark potential in quarkonia systems.
%In my Masters thesis, I tested the Two Higgs Doublet Model of Type II against flavour observables, finding constraints on its parameters, with looks to future works of the Two Higgs Doublet Model in the framework of SM4. 
%Through these courses and projects, I have developed a strong interest in the field of particle physics, flavour physics in particular.
I am a very hard-working individual who will bring passion to my work and happily dedicate myself to my studies to the full extent of my abilities. 


\lettersection{Why Universit\"{a}t Siegen?}
I have come to Universit\"{a}t Siegen because I believe it is the ideal place for me to continue my studies. 
I became aware of Siegen's TP1 research group throughout my Masters thesis through reading many of the group's publications and making use of their results to shape my own research. 
The close alignment of the group's research and publications with what I myself have so far explored makes Siegen an ideal university for me to continue my studies. 
%I know that working with the TP1 group will allow me great opportunities to work with many top researchers in particle physics 
%The group's work in flavour physics aligns closely with what I have explored through my Masters program, and the additional focus on lattice QCD provides further opportunity for me to expand my knowledge base and experience different approaches to the study of particle physics. 
%I have read some of your publications on various B physics calculations with great interest.
%The group's work in Higgs physics and extensions beyond the Standard Model aligns closely with what I have explored through my Masters program. 
The extensive resources of Siegen and its strong focus on international collaboration will provide a great base to develop my skills and work alongside some of the leading experts in the world of particle physics. 
In addition, the area of focus in my PhD project, lattice QCD, is a new area of research to Siegen under Dr. Oliver Witzel, and we hope that it can become an important tool in the research of the TP1 group.
%The extensive resources of TUM and its frequent collaborations with other institutions across the world would provide a great base to develop my skills and work alongside some of the leading experts in the world of particle physics. 
%I believe I could be a great addition to the team at the T31 Group and would very much enjoy the opportunity to take my next steps in physics with you. 

\lettersection{Why Me?}
As I learn more and more about the mysteries of physics, there is one thing I can say with certainty: I need to know more. 
I know that what I have learned so far is just the tip of the iceberg, and I am so eager to continue my learning. 
I am a hard-working, dedicated student who is ready and willing to begin the intensive study and research of a PhD program. 
I will bring the strong communication skills and enjoyment of collaborative work that are very important to academic research. 
Critical thinking is another important aspect which is crucial in performing research and understanding fundamental physics; this is a skill I have used across many disciplines of my life and will apply this skill to all my future pursuits in science.
Coming from Scotland, I look forward to the opportunity of studying internationally at Siegen, where I can experience German culture and integrate myself with the international physics community.
The opportunity to continue my studies and begin to contribute towards the expansion of scientific knowledge would be something most valuable to me, and I relish the chance to dedicate myself fully to this through my PhD position at \uni. 

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
